---
title: "How to use TfidfVectorizer in R ?"
author: "Manish Saraswat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to TfidfVectorizer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this tutorial, we'll look at how to create tfidf feature matrix in R in two simple steps with superml. Superml borrows speed gains using parallel computation and optimised functions from data.table R package. Tfidf matrix can be used to as features for a machine learning model. Also, we can use tdidf features as an embedding to represent the given texts.

## Install 

You can install latest cran version using (recommended):

```{r, eval=FALSE}
install.packages("superml")
```

You can install the developmemt version directly from github using:


```{r, eval=FALSE}
devtools::install_github("saraswatmks/superml")
```

## Sample Data

First, we'll create a sample data. Feel free to run it alongside in your laptop and check the results.

```{r}
library(superml)

# should be a vector of texts
sents <-  c('i am going home and home',
          'where are you going.? //// ',
          'how does it work',
          'transform your work and go work again',
          'home is where you go from to work')

# generate more sentences
n <- 10
sents <- rep(sents, n) 
length(sents)
```

For sample, we've generated 50 documents. Let's create the features now. For ease, superml uses the similar API
layout as python scikit-learn.

```{r}
# initialise the class
tfv <- TfIdfVectorizer$new(max_features = 10, remove_stopwords = FALSE)

# generate the matrix
tf_mat <- tfv$fit_transform(sents)

head(tf_mat, 3)

```

**Few observations:**

* `remove_stopwords = FALSE` defaults to `TRUE`. We set it to `FALSE` since most of the words in our dummy `sents` are stopwords. 
* `max_features = 10` select the top 10 features (tokens) based on frequency.
* The returned matrix is normalised by default, `norm = TRUE` is set by default.
 
 Now, let's generate the matrix using its `ngram_range` features.
 
```{r}
# initialise the class
tfv <- TfIdfVectorizer$new(min_df = 0.4, remove_stopwords = FALSE, ngram_range = c(1, 3))

# generate the matrix
tf_mat <- tfv$fit_transform(sents)

head(tf_mat, 3)

```
 
**Few observations:**

* `ngram_range = c(1,3)` set the lower and higher range respectively of the resulting ngram tokens.
* `min_df = 0.4` says to keep the tokens which occurs in atleast 40% & above of the documents.

## Usage for a Machine Learning Model

In order to use Tfidf Vectorizer for a machine learning model, sometimes it gets confusing as to which method `fit_transform`, `fit`, `transform` should be used to generate tfidf features for the given data. Here's a way to do:

```{r, warning=FALSE}

library(data.table)
library(superml)

# use sents from above
sents <-  c('i am going home and home',
          'where are you going.? //// ',
          'how does it work',
          'transform your work and go work again',
          'home is where you go from to work',
          'how does it work')

# create dummy data
train <- data.table(text = sents, target = rep(c(0,1), 3))
test <- data.table(text = sample(sents), target = rep(c(0,1), 3))
```

Let's see how the data looks like:

```{r}
head(train, 3)

```

```{r}
head(test, 3)
```

Now, we generate features for train-test data:

```{r}

tfv <- TfIdfVectorizer$new(min_df = 0.3, remove_stopwords = FALSE, ngram_range = c(1,3))

# we fit on train data
tfv$fit(train$text)

train_tf_features <- tfv$transform(train$text)
test_tf_features <- tfv$transform(test$text)

dim(train_tf_features)
dim(test_tf_features)

```


We generate 15 features for each of the given data. Let's see how they look:

```{r}
head(train_tf_features, 3)
```

```{r}
head(test_tf_features, 3)
```


Finally, to train a machine learning model on this, you can simply do:

```{r}

# ensure the input to classifier is a data.table or data.frame object
x_train <- data.table(cbind(train_tf_features, target = train$target))
x_test <- data.table(test_tf_features)


xgb <- XGBTrainer$new(n_estimators = 10, objective = "binary:logistic")
xgb$fit(x_train, "target")

predictions <- xgb$predict(x_test)
predictions

```


## Summary

In this tutorial, we discussed how to use superml's tfidfvectorizer to create tfidf matrix and train a machine learning model on it.

